\begin{titlepage}
	\null\vspace{\fill}
	% \input{Files/Abstract}
	\begin{abstract}
		We start with an introduction to Game Theory.
		I have tried to make this report interesting and also covered fundamentals.
		Still, this is just a \emph{glimpse} of an extensive topic like Game Theory.
		This report is divided into parts: Theoretical foundations of Non-Cooperative Game Theory followed by Cooperative Game Theory then Mechanism Design\footnote{only Non-Cooperative Game Theory is covered in Endterm Report, you can always find the updated version \href{https://github.com/paramrathour/Game-Theory/blob/master/Game Theory.pdf}{here}.}.
		% Next, we examine Stochastic Systems.
		% On our way, we will look at corresponding Linear Systems to gain insight onto Game ones.
		% Then, we explore Chaos and Fractals.
		Finally, I encourage you to look at different Games and their exciting results. Check out my Braess's Paradox Video \href{https://drive.google.com/file/d/1DuDqVY9fKFQplJ0WeZ0oq6qUBWRpzKHV/view?usp=sharing}{here}.
	\end{abstract}
	\vspace{\fill}
	\renewcommand{\abstractname}{Acknowledgements}
	% \input{Files/Acknowledgements}
	\begin{abstract}
		This project is a part of the \emph{Summer of Science} of the \emph{Maths and Physics Club IIT Bombay}.
		Thanks to my parents for motivating me to stay productive during this Vacation.
		I would like to express gratitude to my mentor Raj Aryan Agrawal for helping me in my submissions, providing resources.
		The content here is inspired by \cite{book:narahari}, many figures and explanations are directly taken from this.
		And, lastly thanks to you, reader, I have worked hard in making this report, in the hope that this work helps you in some way.
	\end{abstract}
	\vspace{\fill}
\end{titlepage}